Understanding the Popularity of Children's Books: A Data-Driven Analysis

### 2024-12-03 paper/paper.qmd
Update the qmd of the paper

---
title: "Understanding the Popularity of Children's Books: A Data-Driven Analysis"
subtitle: "A Data-Driven Analysis of Cover Type, Page Count, and Publication Period"
author: Zien Gao
thanks: "Code and data supporting this analysis are available at: [GitHub Repository](https://github.com/lauragao75/Understanding-the-Popularity-of-Children-s-Books-A-Data-Driven-Analysis)"
date: today
date-format: long
abstract: "This study examines how different attributes of children's books, such as cover type, page count, and publication period, affect their ratings. Using simulated and cleaned datasets, we apply statistical modeling to identify key factors contributing to higher ratings. The findings provide insights that can assist publishers, authors, and parents in selecting or promoting well-received children's books."
format: pdf
number-sections: true
toc: true
bibliography: references.bib
---

@@

#### Workspace setup ####
library(broom)
library(tidyverse)
library(dplyr)
library(knitr)
library(ggplot2)
library(here)
library(kableExtra)
library(arrow)

#### Load necessary data and models ####
children_model <- readRDS(here("models/simple_model.rds"))
analysis_data <- read_parquet(here("data/analysis_data/clean_books_data.parquet"))
```

@@

The results of our analysis suggest that certain characteristics of children's books are associated with variations in ratings. The linear regression model indicates that hardcover books tend to have higher ratings compared to paperback editions, which could be due to their perceived durability and quality. Regarding page count, books in the "150-299" and "300-499" ranges appear to have higher average ratings, implying that more substantial stories may be favored. Additionally, books published after 2000 tend to receive higher ratings, possibly reflecting evolving preferences or improved production standards in recent years. These findings reveal associations between book attributes and ratings, though they do not imply causation.

@@

@@

We use the statistical programming language R [@citeR] to generate, clean, and analyze the dataset. Our data, sourced from the children's book ratings dataset hosted on GitHub by Alex Cookson, includes metadata such as cover type, publisher, and ratings [@shelter]. The dataset contains information like ISBN, title, author, cover type, pages, and rating, which form the basis for our analysis. Following the approach described by @tellingstories, we focus on attributes that may influence book ratings, such as the type of cover, number of pages, and the original year of publishing.

The libraries used in our analysis include `tidyverse`, `arrow`, `broom`, `ggplot2`, `knitr`, `kableExtra`, and `here`. These libraries enable data manipulation, model building, and visualization, ensuring a comprehensive examination of the dataset to explore relationships between book characteristics and ratings.

## Analysis Dataset
The dataset contains 1000 entries, each representing a children's book, with the following key variables:

- **Covers**: Type of book cover, either Hardcover or Paperback.
- **Pages Range**: Categorized into different ranges, such as "Under 50", "50-149", "150-299", etc.
- **Publish Period**: Divided into four periods: "Before 1950", "1950-1979", "1980-1999", and "2000 and after".
- **Rating**: Book rating on a scale from 1 to 5, representing the perceived quality.

# Model {#sec-model}
To determine the impact of different attributes on book ratings, a simple linear regression model was used:

\`\`\`r
lm(
  rating ~ covers + pages_range + publish_period,
  data = analysis_data
)
\`\`\`

The model predicts book ratings based on the cover type, page count, and publish period. Linear regression was chosen for simplicity and interpretability. Each predictor variable was treated categorically, allowing us to assess how different categories impact the average rating.

# Results {#sec-results}
The regression analysis reveals the impact of each book attribute on the overall rating:

- **Covers**: Hardcover books tend to receive higher ratings than Paperback books.
- **Pages Range**: Books with more pages, particularly those in the "150-299" and "300-499" range, tend to receive higher ratings.
- **Publish Period**: Books published after 2000 tend to have higher ratings compared to earlier periods.

```{r}
#| echo: false
#| warning: false
#| message: false
#| label: fig-coefficients
#| fig-cap: Coefficients of the Linear Regression Model

# Plot coefficients for model
coefficients <- broom::tidy(children_model, conf.int = TRUE)

ggplot(coefficients, aes(x = term, y = estimate)) +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) +
  labs(x = "Predictor Variable", y = "Coefficient Estimate") +
  theme_minimal()
```

@fig-coefficients shows the estimated impact of each attribute on book ratings, with positive coefficients indicating a positive association with higher ratings.

# Discussion {#sec-discussion}
The analysis suggests several factors that may contribute to higher ratings for children's books:

- **Hardcover Advantage**: Hardcover books are generally perceived as higher quality, which may explain their better ratings.
- **More Pages, Higher Ratings**: Books with more pages may indicate more complex stories, which are preferred by parents or older children, leading to better ratings.
- **Modern Books Are Popular**: Books published in recent years (after 2000) tend to have higher ratings, possibly due to better production quality or more contemporary storytelling.

The simplicity of the linear model provides an easy interpretation but also has limitations. Future research could use more sophisticated models to capture non-linear relationships or interactions among variables.

# Conclusion
This study provides insights into the attributes that contribute to higher ratings for children's books. Hardcover editions, books with more pages, and those published after 2000 tend to receive higher ratings. These findings can help publishers, authors, and parents understand the preferences for children’s books and improve decision-making.

Further research could involve using larger datasets and more advanced statistical methods to provide a deeper understanding of what makes a children's book highly rated.

>>>>

---
title: "Understanding the Popularity of Children's Books: A Data-Driven Analysis"
subtitle: "A Data-Driven Analysis of Cover Type, Page Count, and Publication Period"
author: Zien Gao
thanks: "Code and data supporting this analysis are available at: <https://github.com/lauragao75/Understanding-the-Popularity-of-Children-s-Books-A-Data-Driven-Analysis>"
date: today
date-format: long
abstract: "This study investigates the factors influencing children's book ratings, focusing on attributes such as cover type, page count, and publication period. Using simulated and cleaned datasets from various sources, we applied a Bayesian hierarchical linear model to explore these relationships comprehensively. We estimate that hardcover books, books in the 150-299 and 300-499 page ranges, and books published after 2000 have notably higher ratings, providing a clear indication of preferences in children's literature. These insights are critical for publishers, authors, and parents in making informed decisions about book design and selection. The findings highlight important characteristics that contribute to well-received children's literature, aiming to enhance both quality and reader satisfaction."
format: pdf
number-sections: true
toc: true
bibliography: references.bib
---

@@

#### Workspace setup ####
library(broom)
library(tidyverse)
library(dplyr)
library(knitr)
library(ggplot2)
library(here)
library(kableExtra)
library(arrow)
library(modelsummary)

#### Load necessary data and models ####
children_model <- readRDS(here("models/model.rds"))
analysis_data <- read_parquet(here("data/analysis_data/clean_books_data.parquet"))
```

@@

The results of our analysis suggest that certain characteristics of children's books are associated with variations in ratings. The Bayesian model indicates that hardcover books tend to have higher ratings compared to paperback editions, which could be due to their perceived durability and quality. Regarding page count, books in the "150-299" and "300-499" ranges appear to have higher average ratings, implying that more substantial stories may be favored. Additionally, books published after 2000 tend to receive higher ratings, possibly reflecting evolving preferences or improved production standards in recent years. These findings reveal associations between book attributes and ratings, though they do not imply causation.

@@

\newpage

@@

## Data Overview

We use the statistical programming language R [@R] to generate, clean, and analyze the dataset. Our data, sourced from the children's book ratings dataset hosted on GitHub by Timothy A. Cookson [@dataset], includes metadata such as cover type, publisher, and ratings. The dataset contains information like ISBN, title, author, cover type, pages, and rating, which form the basis for our analysis. We focus on attributes that may influence book ratings, such as the type of cover, number of pages, and the original year of publishing.

The libraries used in our analysis include `tidyverse` [@tidyverse], `arrow` [@arrow], `broom` [@broom], `ggplot2` [@ggplot2], `knitr` [@knitr], `kableExtra` [@kableExtra], `here` [@here], and `modelsummary` [@modelsummary]. These libraries enable data manipulation, model building, and visualization, ensuring a comprehensive examination of the dataset to explore relationships between book characteristics and ratings.

## Measurement

To understand the factors influencing the popularity of children's books, we translated various real-world phenomena into measurable attributes for our dataset. The dataset used in this analysis originates from a collection of children’s books that includes detailed metadata about each book, such as cover type, page count, original publication year, and ratings given by readers. Each of these variables represents specific features that could influence a book's popularity, and they were selected to capture different aspects of what makes a book appealing to young readers and their families.

**Cover Type** is one of the key attributes measured. It represents the physical form of the book, categorized into "Hardcover" and "Paperback." This feature is often associated with a book's durability, visual appeal, and market positioning. Hardcover books are typically seen as premium products, potentially giving them an edge in ratings due to perceived quality.

**Page Count** is used to indicate the length of a book and is categorized into five different ranges: "Under 50," "50-149," "150-299," "300-499," and "500 and above." This transformation from a continuous variable to categorical ranges allows us to understand whether readers prefer shorter or longer books, which could affect the overall enjoyment and rating of a book.

**Publication Year** is another important attribute, reflecting the era during which the book was published. This variable was transformed into distinct periods: "Before 1950," "1950-1979," "1980-1999," and "2000 and after." Such categorization helps capture trends over time, as preferences in children's literature may shift due to changing societal norms, advances in education, or evolving cultural values.

Finally, **Ratings** are collected as numeric values ranging from 0 to 5, representing the perceived quality of each book according to its readers. These ratings serve as the core outcome variable in our analysis, allowing us to determine which attributes of children's books are most closely associated with higher reader satisfaction.

Together, these measured attributes offer a comprehensive framework to analyze which factors most influence the popularity of children's books. By taking real-world characteristics, such as the physical form and publication timing of a book, and translating them into well-defined, structured variables, we ensure that our dataset accurately represents elements that are believed to shape the appeal and success of children's literature.

## Outcome Variables

Our analysis focuses on understanding the factors that contribute to higher ratings for children's books. The core outcome variable in this study is the **rating** of each book, which represents the overall popularity and perceived quality. In this section, we explore how ratings are distributed and visualize the relationships between ratings and different book attributes.

### Ratings Distribution

The **ratings** variable represents the average score given to each book, ranging from 0 to 5. Ratings are a key indicator of a book's success and can reflect various dimensions, such as story quality, reader engagement, and production value.

```{r}
#| label: fig-ratings-distribution
#| fig-cap: Distribution of Children's Book Ratings. Shows how the ratings of children's books are generally skewed towards higher values, indicating a general satisfaction with the literature available.
#| echo: false

ggplot(analysis_data, aes(x = rating)) +
  geom_histogram(binwidth = 0.2, fill = "skyblue", color = "black", alpha = 0.7) +
  theme_minimal() +
  labs(x = "Rating (out of 5)", y = "Frequency")
```

@fig-ratings-distribution shows the distribution of ratings across all books in the dataset. We observe that most books tend to have relatively high ratings, clustering around values between 3.5 and 5. This skew towards higher ratings may indicate a general satisfaction with the books or potential bias in how ratings are assigned.

## Predictor Variables

In this section, we describe the predictor variables used in the analysis of children's book ratings. The predictor variables we considered include cover type, page range, and publication period. Each of these variables was analyzed to determine its association with the overall rating of children's books. Below, we present detailed descriptions, graphs, and tables for each predictor.

### Rating by Cover Type

The **cover type** variable represents whether a book is in "Hardcover" or "Paperback." It’s an important feature as the physical presentation of a book can influence reader perception and preferences. Here, we visualize the relationship between cover type and book ratings.

```{r}
#| label: fig-cover-ratings
#| fig-cap: Relationship Between Book Ratings and Cover Type. Illustrates that hardcover books tend to receive slightly higher ratings compared to paperback editions, potentially due to their perceived durability and premium quality.
#| echo: false

# Adding jitter points to show individual data points
ggplot(analysis_data, aes(x = cover, y = rating, fill = cover)) +
  geom_violin(alpha = 0.7) +
  geom_jitter(width = 0.2, alpha = 0.4, color = "black") +
  scale_fill_manual(values = c("darkorange", "dodgerblue")) +
  theme_minimal() +
  labs(x = "Cover Type", y = "Rating (out of 5)")
```

@fig-cover-ratings shows the distribution of ratings by cover type. Hardcover books generally tend to receive slightly higher ratings than paperback books, suggesting that readers may associate the physical sturdiness of hardcover books with higher quality. This could also reflect the fact that hardcovers are often positioned as premium products.

### Rating by Page Range

**Page range** was categorized into five levels: "Under 50", "50-149", "150-299", "300-499", and "500 and above". The goal was to determine if the length of a book influences its rating, as longer books might be perceived as offering a more immersive story.

```{r}
#| label: fig-page-range-ratings
#| fig-cap: Average Ratings by Page Range. Indicates that books with 150-299 pages are more likely to receive higher ratings, potentially reflecting a balance between story depth and accessibility for children.
#| echo: false

# Adding jitter points to show individual data points
ggplot(analysis_data, aes(x = pages_range, y = rating, fill = pages_range)) +
  geom_violin(alpha = 0.7) +
  geom_jitter(width = 0.2, alpha = 0.4, color = "black") +
  theme_minimal() +
  scale_fill_brewer(palette = "Set3") +
  scale_x_discrete(limits = c("Under 50", "50-149", "150-299", "300-499", "500 and above")) +
  scale_fill_discrete(limits = c("Under 50", "50-149", "150-299", "300-499", "500 and above")) +
  labs(x = "Page Range", y = "Rating (out of 5)")
```

@fig-page-range-ratings illustrates the average ratings for different page ranges. It appears that books in the "150-299" range receive higher ratings on average, followed by books in the "300-499" range. This could imply that readers prefer books of intermediate length, as they often strike a balance between offering enough content for engagement without being too lengthy for younger audiences.

### Rating by Publication Period

Books published in different time periods may reflect changing styles, themes, and cultural relevance. The **publication period** variable categorizes books based on their original publication year.

```{r}
#| label: fig-pub-period-ratings
#| fig-cap: Average Ratings by Publication Period. Highlights that books published after 2000 tend to have higher ratings, possibly reflecting evolving preferences and improved production standards.
#| echo: false

# Adding jitter points to show individual data points
ggplot(analysis_data, aes(x = publish_period, y = rating, fill = publish_period)) +
  geom_violin(alpha = 0.7) +
  geom_jitter(width = 0.2, alpha = 0.4, color = "black") +
  theme_minimal() +
  scale_fill_brewer(palette = "Pastel1") +
  scale_x_discrete(limits = c("Before 1950", "1950-1979", "1980-1999", "2000 and after")) +
  scale_fill_discrete(limits = c("Before 1950", "1950-1979", "1980-1999", "2000 and after")) +
  labs(x = "Publication Period", y = "Rating (out of 5)")
```

@fig-pub-period-ratings shows the average ratings for books from different publication periods. Books published in more recent years, particularly after 2000, tend to receive higher ratings. This could reflect improvements in the quality of children's literature, evolving reader preferences, or better production standards. Alternatively, it may indicate that recent books are simply more relevant to today's audiences.

## Summary

Overall, we observe interesting patterns between book attributes and ratings. The physical characteristics of books, such as cover type and length, appear to play a role in how well they are rated. Similarly, the time of publication also seems to impact the perceived quality of a book. These insights suggest that certain characteristics may enhance a book's appeal, providing valuable information for authors and publishers seeking to create well-received children’s books.

\newpage

# Model {#sec-model}

The goal of our modeling strategy is twofold. Firstly, we aim to quantify the relationship between book characteristics (such as cover type, page range, and publication period) and their respective ratings. Secondly, we seek to identify which of these characteristics are the most influential in driving higher ratings for children's books. This will help inform authors, publishers, and readers about what features may contribute to a book's popularity and perceived quality.

Here, we briefly describe the Bayesian analysis model used to investigate these relationships. We employed a Bayesian hierarchical linear model, which is particularly suitable for our study because it allows us to incorporate prior knowledge and account for potential variability between different book categories. This model provides more nuanced insights compared to classical statistical models, particularly when dealing with smaller datasets or datasets that might have underlying group structures.

The dependent variable in our model is the book rating (on a scale of 0 to 5), while the independent variables are the predictor variables discussed earlier: cover type, page range, and publication period. By using Bayesian modeling, we incorporate prior distributions for each of the coefficients, allowing for uncertainty in the estimates to be captured directly.

Background details and model diagnostics, including convergence checks and posterior predictive checks, are provided in [Appendix - @sec-model-details]. These diagnostics help ensure the robustness and reliability of our results, verifying that the model appropriately fits the data and that inferences drawn are trustworthy.

## Model Assumptions and Limitations

The Bayesian hierarchical linear model makes several assumptions that should be considered when interpreting the results:

1. **Normality of Errors**: The model assumes that the residuals (errors) are normally distributed. This means that the difference between the predicted and observed values follows a normal distribution, which may not always hold, particularly if the data contains outliers or non-linear patterns.

2. **Linearity**: The relationship between the predictor variables (cover type, page range, and publication period) and the outcome variable (ratings) is assumed to be linear. If the true relationship is non-linear, the model may not accurately capture it.

3. **Homogeneity of Variance**: The model assumes that the variance of errors is constant across all levels of the predictor variables. Any deviation from this assumption (e.g., heteroscedasticity) may affect the reliability of the estimates.

4. **Independence of Observations**: The observations are assumed to be independent of one another. This means that each book rating is assumed to be independent, which might not always be the case if, for example, multiple ratings are influenced by a common author or publisher.

5. **Priors**: The priors used for the model are weakly informative, meaning that they have little influence unless the data strongly supports them. This helps to regularize the estimates but could still introduce some bias if the prior assumptions are incorrect.

### Limitations

1. **Data Quality**: The quality of the model's results depends heavily on the quality of the data. Missing data, inaccuracies in reported ratings, or inconsistencies in book characteristics could introduce bias into the analysis.

2. **Limited Scope**: The model only considers a limited set of book attributes (cover type, page range, publication period). Other factors, such as author reputation, book awards, or illustrations, may also influence ratings but are not included here.

3. **Causality**: The model identifies associations between book characteristics and ratings but does not establish causation. Higher ratings may be linked to certain characteristics, but it is not necessarily true that changing these characteristics will directly improve a book's rating.

4. **Posterior Convergence**: The reliability of Bayesian inference depends on the convergence of the Markov chains. If the chains do not converge well, the inferences drawn may be unreliable.

## Model Set-up

Define \(y_i\) as the average rating for book \(i\). Then \(eta_1\) represents the effect of cover type, \(eta_2\) represents the effect of page range, and \(eta_3\) represents the effect of publication period.

```{=tex}
\[
egin{align} 
y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
\mu_i &= \alpha + eta_1(CoverType_i) + eta_2(PageRange_i) + eta_3(PublicationPeriod_i) \\
\alpha &\sim \mbox{Normal}(0, 2.5) \\
eta_1 &\sim \mbox{Normal}(0, 2.5) \\
eta_2 &\sim \mbox{Normal}(0, 2.5) \\
eta_3 &\sim \mbox{Normal}(0, 2.5) \\
\sigma &\sim \mbox{Exponential}(1)
\end{align}
\]
```

We run the model in R [@R] using the `rstanarm` package [@rstanarm]. We use the default priors from `rstanarm`.

### Model Justification

We expect a positive relationship between certain book characteristics and higher ratings. Specifically, hardcover books may receive higher ratings due to their perceived durability and premium quality. Medium-length books may be preferred for their balance between story depth and accessibility. Books published more recently may receive higher ratings, potentially reflecting changes in reader preferences or improved production standards.

\newpage

# Results {#sec-results}

The primary goal of our analysis was to determine the factors that influence the ratings of children's books. Below, we summarize the findings from the Bayesian hierarchical linear model and interpret their practical implications for understanding the popularity of children's books.

## Summary of Model Results

The summary statistics for our model parameters, presented in the appendix (Appendix - @sec-model-details), highlight key insights about the influence of book attributes on ratings.

### Summary Statistics

To provide context for the model results, we present some key summary statistics of the dataset used in the analysis. This includes the average rating, distribution of book types, and the breakdown of page ranges and publication periods.

```{r}
#| label: tbl-summary-statistics
#| echo: false
#| tbl-cap: "Summary statistics of the children's book dataset"

library(dplyr)
summary_stats <- analysis_data %>%
  summarise(
    `Average Rating` = round(mean(rating, na.rm = TRUE), 2),
    `Number of Hardcover Books` = sum(cover == "Hardcover"),
    `Number of Paperback Books` = sum(cover == "Paperback")
  )

# Get counts for page ranges and publication periods
pages_range_count <- analysis_data %>%
  count(pages_range) %>%
  rename(Metric = pages_range, Value = n) %>%
  mutate(Metric = paste("Page Range:", Metric))

publish_period_count <- analysis_data %>%
  count(publish_period) %>%
  rename(Metric = publish_period, Value = n) %>%
  mutate(Metric = paste("Publication Period:", Metric))

# Combine all summary statistics into one table
combined_summary <- bind_rows(
  summary_stats %>% pivot_longer(everything(), names_to = "Metric", values_to = "Value"),
  pages_range_count,
  publish_period_count
)

# Display the combined summary statistics table
knitr::kable(combined_summary, caption = "Combined summary statistics of the children's book dataset, including average ratings, distribution of cover types, page ranges, and publication periods.")
```

### Model Summary

The model included predictors such as **cover type** (hardcover vs. paperback), **page range**, and **publication period**. From the posterior summaries, we can infer several important relationships:

1. **Cover Type**: Books with a hardcover format tend to have slightly higher ratings than paperback editions. The estimated effect size is positive, indicating a preference for hardcover, which may be related to perceived durability and quality.

2. **Page Range**: Books with more pages, specifically in the range of **150-299 pages**, show a positive association with higher ratings. This finding implies that books with more substantial content are generally favored, though extremely lengthy books (over 500 pages) do not necessarily receive better ratings.

3. **Publication Period**: Books published in more recent periods, particularly after **2000**, are associated with higher ratings. This suggests a shift in consumer preferences towards modern content or improvements in book quality in recent decades.

These results are illustrated in @fig-results-effects, where each plot represents the posterior distributions of the effects of cover type, page range, and publication period on ratings.

### Regression Results Table

The regression table @tbl-regression-results provides the estimated effects of each predictor variable on children's book ratings.

## Interpretation of Results

These findings suggest that certain characteristics of children's books are associated with varying levels of consumer appreciation, as reflected by their ratings. For instance, the preference for **hardcover editions** may indicate that buyers value quality and durability in children's books, possibly because these books are meant to be handled repeatedly by young readers.

The association with **page range** suggests that books providing moderate-length stories (150-299 pages) are highly valued. This range may offer enough depth for engaging storytelling without overwhelming younger readers.

Lastly, the preference for books published **after 2000** may indicate evolving preferences in children's literature. This could be due to the integration of more diverse themes and characters, better illustrations, or more modern narratives that resonate well with today's audiences.

These findings could help **authors**, **publishers**, and **parents** understand what characteristics are linked to better reception in children's literature, ultimately guiding decisions on book production, marketing, and selection.

\newpage

# Discussion {#sec-discussion}

## Factors Influencing Children's Book Ratings

In our study, we identified several key factors that influence children's book ratings. The **cover type**, **page range**, and **publication period** were found to significantly impact how books are rated. This section will delve deeper into these factors, examining why they may play a crucial role in determining a book's popularity.

The preference for **hardcover books** can be attributed to their perceived durability and quality. Since children's books are often read repeatedly, a hardcover format might offer more resilience, making it a preferred choice among parents and educators. This preference highlights an important aspect of consumer behavior when it comes to children's literature—practicality and longevity of the product are crucial.

The association between **page range** and ratings is another significant finding. Books in the **150-299 pages** range received higher ratings, suggesting that consumers value content that strikes a balance between being engaging and not overly lengthy. This page range might provide just the right amount of depth for storytelling, making the books suitable for young readers without overwhelming them. The implication here is that content length plays a critical role in the perceived quality and enjoyment of children's books.

Our analysis also revealed that books published **after 2000** tend to have higher ratings. This finding may be indicative of evolving tastes and preferences in children's literature, as well as improvements in book quality over the years. It is possible that newer books incorporate more diverse themes, modern storytelling techniques, and better visual appeal, all of which resonate well with today's readers. The shift in consumer preferences towards newer books could also be related to changes in societal values and expectations. For instance, children's literature has seen a growing emphasis on inclusivity and representation in recent years. Books that reflect diverse experiences and characters may be more likely to receive higher ratings, as they provide young readers with stories they can relate to and learn from. This trend underscores the importance of staying relevant and adapting to the changing landscape of children's literature.

## Practical Implications for Authors and Publishers

The insights gained from this study have practical implications for **authors**, **publishers**, and **booksellers**. Understanding that **hardcover formats** are generally preferred can help publishers decide on the most marketable format for their books. Additionally, targeting the **150-299 pages** range may increase the likelihood of positive reception, as it appears to be the sweet spot for engaging yet manageable content.

For authors, being mindful of the themes and topics that resonate with modern audiences is crucial. Books that reflect contemporary issues, promote inclusivity, and feature diverse characters are more likely to receive favorable ratings. Publishers can also use this information to guide their acquisition and production decisions, ensuring that the books they bring to market align with current consumer preferences.

Ultimately, the findings of this study contribute to a better understanding of what makes children's books popular and well-rated. By considering factors such as **cover type**, **page range**, and **publication period**, stakeholders in the children's literature market can make informed decisions to enhance the quality and appeal of their offerings.

## Weaknesses and Next Steps

While our study provides valuable insights, there are some limitations that should be acknowledged. One of the main weaknesses is that our dataset may not fully represent all children's books, especially those published outside the mainstream market or those that are self-published. The analysis is based on a subset of available books, which could introduce biases in our findings.

Another limitation is the lack of detailed reader demographics. Ratings can be influenced by the age, preferences, and reading habits of the reviewers, which were not accounted for in our model. Future research could incorporate demographic information to better understand how different groups perceive children's books.

In terms of next steps, expanding the dataset to include more books, especially those from diverse publishers and formats, would help improve the robustness of the analysis. Additionally, exploring other features, such as the presence of illustrations, themes, or author reputation, could provide a more comprehensive understanding of the factors influencing book ratings.

Finally, incorporating qualitative data, such as reader reviews, could help capture aspects of children's books that are not easily quantifiable but still contribute to their popularity and success.

\newpage
\appendix

# Appendix - Model Details {#sec-model-details}

## Regression Model Summary

```{r}
#| label: tbl-regression-results
#| echo: false
#| tbl-cap: "Regression model summary for predicting children's book ratings, including estimated coefficients and credible intervals."

model_summary <- modelsummary(
  list(
    "Children's Book Model" = children_model
  ),
  statistic = "mad",  # Using median absolute deviation
  fmt = 2,              # Format for rounding numbers
  output = "kableExtra"  # Use kableExtra for better formatting
)

# Display the model summary
model_summary
```

## Convergence Diagnostics

To ensure that the Bayesian hierarchical linear model has converged properly, we used multiple convergence diagnostics. The primary convergence diagnostic used is the **Gelman-Rubin statistic** (R-hat). The R-hat value should ideally be close to 1, indicating that the Markov chains have mixed well and reached convergence. Any R-hat value significantly above 1 suggests non-convergence and needs further investigation.

```{r}
#| label: rhat-diagnostics
#| echo: false
#| fig-cap: "Gelman-Rubin convergence diagnostic (R-hat) values for each model parameter. All values are close to 1, indicating that the Markov chains have mixed well and achieved convergence."

# Plot R-hat values for all parameters
plot(children_model, plotfun = "rhat")
```

### Trace Plots

Another convergence diagnostic involves examining trace plots. Trace plots show the sampled values of each parameter across iterations for each Markov chain. Well-mixed chains with no clear trends suggest that the model has converged.

```{r}
#| label: trace-plot
#| echo: false
#| fig-cap: "Trace plots for key parameters across the Markov chains, showing well-mixed chains with stable values. The lack of discernible patterns or trends confirms that convergence has been reached."

# Trace plot for key parameters in the model
plot(children_model, plotfun = "trace")
```

## Posterior Predictive Checks

Posterior predictive checks are used to assess the goodness-of-fit of the Bayesian model. By simulating data from the posterior distribution, we can compare the simulated data to the observed data to determine if the model adequately represents the data.

```{r}
#| label: posterior-checks
#| echo: false
#| fig-cap: "Posterior predictive checks showing a comparison between the observed data and simulated data generated from the model's posterior distribution. This helps evaluate whether the model adequately captures the key features of the observed data."

# Posterior predictive check for the Bayesian model
pp_check(children_model)
```

## Summary Statistics for Posterior

Below is a summary table of the key parameters in the model, including the estimated means, standard deviations, and 95% credible intervals.

```{r}
#| label: posterior-summary
#| echo: false
#| fig-cap: "Summary statistics of the posterior distributions for key model parameters, including posterior means, standard deviations, and 95% credible intervals, which provide insights into the central tendencies and uncertainties of the parameter estimates."

# Summary of the posterior distributions
summary(children_model)
```

### Posterior Density Plots

Posterior density plots provide a visual representation of the uncertainty in the model parameters. The density plots show the distribution of possible values for each parameter, which helps in understanding the spread and central tendency.

```{r}
#| label: fig-results-effects
#| echo: false
#| fig-cap: "Posterior density plots for each model parameter, providing a visual representation of the uncertainty in the parameter estimates. The density curves illustrate the range and central tendency of plausible values derived from the data and priors."

plot(children_model, plotfun = "dens")
```

\newpage

# References
